Parameter precision in economic growth models inspired by Ecological Economics

### 2015-10-12 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
set up parent and child docs -- eliminate text from child doc

@@

>>>>

%%%% Import Analysis chunks

<<child="TestChild.Rnw", eval=TRUE>>=
@

<<child="../EcolEcon_2015A.Rnw", eval=TRUE>>=
@

<<include=FALSE>>=
knitr::opts_chunk$set(include = TRUE)
@

<<replay, include=TRUE, echo=FALSE>>=
<<Graphs_CESlek-fitted>>
@

@@

Looking at boostrap distribution of a parameter.
<<>>=
ggplot( aes(x = lambda, color = method), data = resampledCoeffsCD) + geom_line(stat="density") + facet_grid( foo ~ Country, scales = "free" ) 
mod <- resampleModelsCD[["PT.adjusted.noE.CD"]][["orig"]]
coef(summary(mod))

@
